Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-13 writeups/proposal/proposal.tex
foo
Former-commit-id: 8b9532f7544884a7bbf7075940f87b014c3a3159 [formerly d977002407e4e8bdc41f3174cb98a7d63082b353]
Former-commit-id: fef35ede069e88f298d7b286bbbf3fbaa973f4dd

For vector-based systems, each word is represented by an environment vector $e_{j}$ that is nearly orthogonal to all other words' environment vectors.
The number of dimensions for these vectors is much less than the number of rows in a full word co-occurrence matrix, which is how vector-based systems represent information in a much more compact space.
Paired with each environment vector ($e_{i}$) is a memory vector ($m_{i}$) that contains the summed representation of all other environment vectors that have co-occurred with that $e_{i}$ environment vector.
These memory vectors can contain environment vectors from bag-of-words co-occurrence information ($c_{i}$) and word order information ($o_{i}$), which can be combined into a single representation ($m_{i}$).
Over time, memory vectors accumulate a distributed representation of the most common environment vectors that co-occurred with them.

@@

New vectors generated by circular convolution are uncorrelated with all other environment vectors and have the same length.
This allows the word order information and unordered context information for a chunk to be aggregated and represented in the same memory vector.
Quite simply, the different types of memory vectors can be summed to create a single memory vector representation for each chunk (i.e., $m_{j} = c_{j} + o_{j}$).

@@

\textcite{Jones2007} created the BEAGLE vector-based memory representation.
Each memory vector ($m_{j}$) is a summed representation of unordered and ordered word co-occurrences ($c_{j} + o_{j}$).
This model uses circular convolution and circular correlation as a way to encode and decode word order.
BEAGLE performed similar to LSA when trained on the TASA and tested on the TOEFL (55.6\% compared to 55.3\%).
Also, BEAGLE with unordered context and word order was more correlated to the WordNet synonym database than LSA (-.311 compared to -.165).
Further, it was shown that incorporating word-order information into the same representation resulted in minimal data loss (less than 1 percent of total predictive variance).
This model provided an efficient algorithm for using a single representation for unordered and ordered information that showed performance similar to if not better than LSA.

>>>>

For vector-based systems, each word is represented by an environment vector $e_{i}$ that is nearly orthogonal to all other words' environment vectors.
The number of dimensions for these vectors is much less than the number of rows in a full word co-occurrence matrix, which is how vector-based systems represent information in a much more compact space.
Paired with each environment vector ($e_{i}$) is a memory vector ($m_{i}$) that contains the summed representation of all other environment vectors that have co-occurred with that $e_{i}$ environment vector.
These memory vectors can contain environment vectors from bag-of-words co-occurrence information ($c_{i}$) and word order information ($o_{i}$), which can be combined into a single representation ($m_{i}$).
Over time, memory vectors accumulate a distributed representation of the most common environment vectors that co-occurred with them.

@@

New vectors generated by circular convolution are uncorrelated with all other environment vectors and have the same length.
This allows the word order information and unordered context information for a chunk to be aggregated and represented in the same memory vector.
Quite simply, the different types of memory vectors can be summed to create a single memory vector representation for each chunk (i.e., $m_{i} = c_{i} + o_{i}$).

@@

\textcite{Jones2007} created the BEAGLE vector-based memory representation.
Each memory vector ($m_{i}$) is a summed representation of unordered and ordered word co-occurrences ($c_{i} + o_{i}$).
This model uses circular convolution and circular correlation as a way to encode and decode word order.
BEAGLE performed similar to LSA when trained on the TASA and tested on the TOEFL (55.6\% compared to 55.3\%).
Also, BEAGLE with unordered context and word order was more correlated to the WordNet synonym database than LSA (-.311 compared to -.165).
Further, it was shown that incorporating word-order information into the same representation resulted in minimal data loss (less than 1 percent of total predictive variance).
This model provided an efficient algorithm for using a single representation for unordered and ordered information that showed performance similar to if not better than LSA.
